\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{changepage}
\usepackage{geometry}
\geometry{
a4paper,
left=30mm,
right = 30mm,
top=30mm,
bottom = 30mm,
}



\newenvironment{indentall}{\begin{adjustwidth}{2cm}{}}{\end{adjustwidth}}

\title{Puppeteer - Technical Specification}
\pagenumbering{gobble}

\begin{document}
\maketitle

\vspace*{\fill}

\subsection*{Group Members}
\hspace*{\fill}
\newline Sandra Andersson \hfill Dev
\newline Carl Appelkvist \hfill Dev
\newline Ludvig Björk Förare \hfill Dev
\newline Anton Jonsson \hfill Dev
\newline Kristoffer Lundgren \hfill Dev
\newline Filip Rehnman \hfill Dev
\newline Philip Stenmark \hfill Dev
\newline Benjamin Vesterlund \hfill Dev
\newline Oscar Leiner Olsson \hfill Artist
\newline Gustav Mårdestam \hfill Artist
\newline Robert Ringholm \hfill Artist
\newline
\hspace*{\fill}

\begin{center}
\begin{tabular}{|c|c|c|c|} 
\hline
Revision & Date & Name & Comment \\
\hline
A & 2019-04-11 & Anton Jonsson & Milestone 2 \\ 
&&   Philip Stenmark &\\
&& Kristoffer Lundgren &\\
\hline
B & 2019-04-16 & Sandra Andersson & Revised for implementation of player,\\ 
&&   Philip Stenmark & interaction, weapons and health. \\
\hline
C & 2019-04-18 & Sandra Andersson & Revised for implementation of traps. \\
\hline
D & 2019-05-24 & Anton Jonsson & Implemented into \LaTeX \\
\hline
E & 2019-05-24 & All developers & Final cleanup for Milestone 5 \\
\hline
\end{tabular}
\end{center}





\newpage
\tableofcontents

\newpage
\pagenumbering{arabic}
\section{Game Mechanics}
\subsection{Platform and OS}
Windows 7 or higher (64-bit only)
\newline i7 - 6700k @ 4.00GHz or AMD equivalent
\newline Nvidia Geforce GTX-980 Ti or AMD equivalent
\newline 16 GB RAM

\subsection{External Code}
Unity 2018
\newline Oculus SDK for VR-support
\newline Mirror by vis2k for networking
\newline FMOD for sound

\newpage

\subsection{Game Objects}
\subsubsection{Level}
Components
\begin{itemize}
	\item LevelBuilder
	\newline Attributes
	\begin{itemize}
		\item List<GameObject> MultiDoorRooms
		\item GameObject StartRoom
		\item GameObject GoalRoom
		\item GameObject Door
		\item Int RoomsToSpawnBeforeDeadEndRooms
		\item List<RoomCollider> roomColliderPosit	ions
		\item Queue<AnchorPoint> openDoorQueue
		\item List<GameObject> roomsToBePlaced
		\item RoomTreeNode startNode
		\item GameObject parent
	\end{itemize}
	Methods
	\begin{itemize}
		\item Start
		\item RandomizeRooms
		\item SpawnRooms
		\item SpawnRoomsOnNetwork
		\item GetRooms
		\item ConnectDoorsInRoomIfPossible
	\end{itemize}
\newpage
	\item ItemSpawning
	\newline Attributes
	\begin{itemize}
		\item uint NumberOfSpawns
		\item List<SnapPointBase> spawners
		\item GameObject level
		\item List<GameObject> WeaponList
		\item GameObject localSpawner
		\item ItemsToSpawn
	\end{itemize}
	Methods
	\begin{itemize}
		\item Awake
		\item FindSnapPoints
		\item SpawnItems
		\item RpcSetParent
		\item GetRandom
		\item SpawnWeapon
		\item SpawnAmmo
		\item SpawnPowerUp
		\item SpawnMedkit
		\item SpawnItem
	\end{itemize}
\end{itemize}

\subsubsection{Room}
Room should be synced with Mirror
\newline Tag
\begin{itemize}
	\item Connectable
\end{itemize}
Components
\begin{itemize}
	\item CooldownComponent
	\newline Attributes
	\begin{itemize}
		\item float CooldownTime
		\item bool Available
	\end{itemize}
	Methods
	\begin{itemize}
		\item get/set Available
		\item StartCooldown
	\end{itemize}
	\item Mesh Renderer
	\item Box Collider
\end{itemize}

\subsubsection{Puppet}
Tag
\begin{itemize}
	\item Player
\end{itemize}
Components
\begin{itemize}
	\item HealthComponent
	\newline Attributes
	\begin{itemize}
		\item uint Health
		\item uint MaxHealth
		\item uint MaxRegenHealth
		\item float MaxRegenRatio
		\item float MaxReviveRatio
		\item uint RegenSpeed
		\item uint RegenDelay
		\item bool AllowRegen
	\end{itemize}
	Methods
	\begin{itemize}
		\item Damage
		\item Revive
		\item AddDeathAction
		\item RemoveDeathAction
	\end{itemize}
	\item InteractionController
	\newline Attributes
	\begin{itemize}
		\item Lookahead
	\end{itemize}
	Methods
	\begin{itemize}
		\item Update
	\end{itemize}
	\item Interactable (acts as base class for all in-level interactable items)
	\newline Methods
	\begin{itemize}
		\item OnInteractBegin
		\item OnInteractEnd
		\item OnRaycastEnter
	\end{itemize}
	\item Image (UI image for compass)
\newpage
	\item PowerUpBase (acts as base class for all power-ups)
	\newline Attributes
	\begin{itemize}
		\item int Duration
	\end{itemize}
	Methods
	\begin{itemize}
		\item OnActivate
		\item OnComplete
	\end{itemize}
	\item StaminaPower : PowerUpBase
	\newline Attributes
	\begin{itemize}
		\item float SpeedModifier
	\end{itemize}
	\item InvisibilityPower : PowerUpBase
	\item NavigationPower : PowerUpBase
	\item SnifferPower : PowerUpBase
	\item PlayerController : Interactable
	\newline Attributes
	\begin{itemize}
		\item float MovementSpeed
		\item float AccelerationRate
		\item float SprintSpeed
		\item float MaxStamina
		\item bool DisableInput
		\item float JumpForce
		\item float JumpRayLength
		\item float MouseSensitivity
		\item bool HasMedkit
		\item GameObject CurrentWeapon
		\item int Ammunition
		\item bool CanShoot
	\end{itemize}
	Methods
	\begin{itemize}
		\item Update
		\item FixedUpdate
	\end{itemize}
	\item Mesh Renderer
	\item Rigidbody
	\item Capsule Collider (For collision detection)
	\item Animator
\end{itemize}

\subsubsection{Puppeteer}
Components
\begin{itemize}
	\item Mesh Renderer
	\item GrabTool
	\newline Attributes
	\begin{itemize}
		\item LevelBuilder level
		\item int SnapDistance
		\item float RaycastDistance
		\item float LiftHeight
		\item float LiftSpeed
		\item bool EnableMovement
		\item GameObject sourceObject
		\item GameObject selectedObject
		\item GameObject guideObject
		\item AnchorPoint bestSrcPoint
		\item AnchorPoint bestDstPoint
		\item RoomInteractable lastHit
		\item Vector3 grabOffset
		\item RoomTreeNode firstParentNode
	\end{itemize}
	Methods
	\begin{itemize}
		\item Start
		\item Update
		\item Pickup
		\item Drop
		\item UpdatePositions
		\item FindNearestOpenDoor
		\item CanConnect
		\item MouseToWorldPosition
	\end{itemize}
\newpage
	\item ItemGrabTool
	\newline Attributes
	\begin{itemize}
		\item GameObject[] HudItems
		\item Button (All HUD buttons used for the spawning of items and enemies)
		\item GameObject (All the items that can be spawned by the puppeteer)
	\end{itemize}
	Methods
	\begin{itemize}
		\item Start
		\item Update
		\item SetPrices
		\item ClientUpdate
		\item Pickup
		\item Drop
		\item FindNearestFreePoint
		\item CanBePlaced
	\end{itemize}
\end{itemize}

\subsubsection{Enemy}
Tag
\begin{itemize}
	\item Enemy
\end{itemize}
Components
\begin{itemize}
	\item HealthComponent
	\newline Attributes
	\begin{itemize}
		\item uint Health
		\item uint MaxHealth
		\item uint MaxRegenHealth
		\item float MaxRegenRatio
		\item float MaxReviveRatio
		\item uint RegenSpeed
		\item uint RegenDelay
		\item bool AllowRegen
		\item bool Downed
	\end{itemize}
	Methods
	\begin{itemize}
		\item Damage
		\item Revive
		\item AddDeathAction
		\item RemoveDeathAction
	\end{itemize}
\newpage
	\item PathFinderComponent
	\newline Attributes
	\begin{itemize}
		\item bool UseRootMotion
		\item float MovementSpeed
		\item float RotationSpeed
		\item float LegHeight
		\newline
		\item int MaxRecursionDepth
		\item Vector3 TransformRaycastOffset
		\item float NodeArrivalMargin
		\item bool PathfindDebug
		\newline
		\item float RaycastAvoidDistance
		\item float RaycastAvoidAngle
		\item float RaycastAvoidWeight
		\item float MinionAvoidDistance
		\item bool ObstacleAvoidDebug
		\newline
		\item float MinVelocityThreshold
		\item float StuckTimeThreshold
		\item float UnstuckRadius
		\newline
		\item float DoorInteractRange
		\item float ForceSmoothingValue
		\item float ClampValue
		
	\end{itemize}
	Methods
	\begin{itemize}
		\item MoveTo
		\item Stop
	\end{itemize}
\newpage
	\item StateMachine
	\newline Attributes
	\begin{itemize}
		\item uint tickRate
		\item bool MinionType
		\item EnemySpawner Spawner
		\item HealthComponent TargetEntity
		\item PathfinderComponent PathFinder
		\item List GameObject Puppets
		\item float AttackCooldown
		\item uint AttackDamage;
		\item float AttackRange
		\item float AttackEscapeDistance
		\item float ChargeAccelerationSpeed
		\item float StartChargeSpeed
		\item int ChargeDamageMultiplier
		\item Collider[] HitColliders
		\item float AggroDropTime
		\item float InstantAggroRange
		\item float ConeAggroRange
		\item float FOVConeAngle
		\item float MinIdleTime
		\item float MaxIdleTime
		\item Vector3 RaycastOffset
		\item bool debug
		\item float ChooseCurrentRoomChance
	\end{itemize}
	Methods
	\begin{itemize}
		\item SetState
		\item Update
		\item CheckProximity
		\item Die
		\item Despawn
		\item Attack
		\item WithinCone
		\item RemoveY
		\item getNearbyDestination
		\item RoomContainsPlayer
	\end{itemize}
\newpage
	States (classes)
	\begin{itemize}
		\item AttackState
		\newline Methods
		\begin{itemize}
			\item Enter
			\item Run
			\item Exit
		\end{itemize}
		\item ReturnToSpawnerState
		\newline Methods
		\begin{itemize}
			\item Enter
			\item Run
			\item Exit
		\end{itemize}
		\item WanderState
		\newline Methods
		\begin{itemize}
			\item Enter
			\item Run
			\item Exit
		\end{itemize}
		\item SeekState
		\newline Methods
		\begin{itemize}
			\item Enter
			\item Run
			\item Exit
		\end{itemize}
		\item IdleState
		\newline Methods
		\begin{itemize}
			\item Enter
			\item Run
			\item Exit
		\end{itemize}
		\item BigAttackState
		\newline Methods
		\begin{itemize}
			\item Enter
			\item Run
			\item Exit
		\end{itemize}
		\item ChargeAttackState
		\newline Methods
		\begin{itemize}
			\item Enter
			\item Run
			\item Exit
		\end{itemize}
	\end{itemize}
	\item Network Transform
	\item Network Identity
	\item Network Animator
	\item Minion Sounds
	\item Studio Event Emitter
	\item Rigidbody
	\item Capsule Collider
	\item Animator
\end{itemize}

\subsubsection{EnemySpawner}
Components
\begin{itemize}
	\item EnemySpawner
	\newline Attributes
	\begin{itemize}
		\item GameObject EnemyPrefab
		\item GameObject spawnedEnemies
		\item bool TankSpawner
		\item int MaxEnemyCount
		\item Transform spawnPoint
		\item int MinDelay
		\item int MaxDelay
		\item List<StateMachine> LocalMinions
		\item List<StateMachine> AllMinions
		\item Transform MinionContainer
	\end{itemize}
	Methods
	\begin{itemize}
		\item Start
		\item Spawn
		\item CmdOnTakeDamage
		\item RpcPlayAnimation
		\item OnDeath
	\end{itemize}
	\item Transform
	\item Network Identity
	\item Snap Fucntionality
	\item Custom Network Transform
	\item Enemy Spawner Sounds
	\item Puppeteer Item Sounds
\newpage
	\item HealthComponent
	\newline Attributes
	\begin{itemize}
		\item uint Health
		\item uint MaxHealth
		\item uint MaxRegenHealth
		\item float MaxRegenRatio
		\item float MaxReviveRatio
		\item uint RegenSpeed
		\item uint RegenDelay
		\item bool AllowRegen
	\end{itemize}
	Methods
	\begin{itemize}
		\item Damage
		\item Revive
		\item AddDeathAction
		\item RemoveDeathAction
	\end{itemize}
	\item Box Collider
\end{itemize}

\subsubsection{Weapon}
Tag
\begin{itemize}
	\item Weapon
\end{itemize}
Components
\begin{itemize}
	\item WeaponComponent : Interactable
	\newline Attributes
	\begin{itemize}
		\item int Capacity
		\item int LiquidLeft
		\item int LiquidPerRound
		\item float FiringSpeed
		\item int Damage
		\item float Spread
		\item float RecoilAmount
		\item float ReloadTime
		\item int NumberOfShots
	\end{itemize}
	Methods
	\begin{itemize}
		\item Use
		\item Reload
		\item OnInteractBegin
		\item OnRaycastEnter
	\end{itemize}
	\item Mesh Renderer
\end{itemize}

\subsubsection{Trap}
Tag
\begin{itemize}
	\item Trap
\end{itemize}
Components
\begin{itemize}
	\item TrapComponent
	\newline Attributes
	\begin{itemize}
		\item uint Damage
		\item float ActivationTime
		\item float DestroyTime
		\item List<GameObject> Puppets
		\item Animator Anim
	\end{itemize}
	Methods
	\begin{itemize}
		\item TrapTimer
		\item DestroyTimer
		\item ActivateAnim
		\item OnTriggerEnter
		\item OnTriggerStay
		\item ActivateTrap
		\item DestroyTrap
	\end{itemize}
	\item Box Collider
	\item BasicTrap : TrapComponent
	\item BearTrap : TrapComponent
	\item BearInteract : Interactable
	\item FakeItem : Interactable
	\item SnapFunctionality
	\item Mesh Renderer
	\item Animator
\end{itemize}

\newpage

\subsubsection{Door}
Tag
\begin{itemize}
	\item Door
\end{itemize}
Components
\begin{itemize}
	\item DoorComponent : Interactable
	\newline Attributes
	\begin{itemize}
		\item (private)bool locked
		\item (public with getter and setter)bool Locked
		\item Float RotationSpeed
		\item Float openAngle
		\item Float defaultAngle
		\item Vector3 adjustmentVector
		\item Float currentAngle
		\item Bool open
	\end{itemize}
	Methods
	\begin{itemize}
		\item Start
		\item OnInteractBegin
		\item FixedUpdate
		\item OnInteractEnd
		\item OnRaycastEnter
	\end{itemize}
	\item Mesh Renderer
	\item Box Collider
\end{itemize}

\subsubsection{Compass}
Components
\begin{itemize}
	\item CompassComponent
	\newline Attributes
	\begin{itemize}
		\item List<GameObject> targets
		\item Vector3 north
	\end{itemize}
	Methods
	\begin{itemize}
		\item AddObject
		\item RemoveObject
		\item Update
	\end{itemize}
\end{itemize}

\subsubsection{PowerUpRecharge}
Components
\begin{itemize}
	\item MeshRenderer
	\item Recharge/Refill : Interactable (used to refill the player’s power)
	\item Box Collider
\end{itemize}

\subsubsection{Medkit}
Components
\begin{itemize}
	\item Medkit : interactable
	\newline Methods
	\begin{itemize}
		\item OnInteractBegin
		\item OnInteractEnd
		\item OnRaycastEnter
	\end{itemize}
\end{itemize}

\newpage

\subsubsection{HUD}
Components
\begin{itemize}
	\item HUDScript
	\newline Attributes
	\begin{itemize}
		\item Transform Owner
		\item RectTransform HealthBarFill
		\item RectTransform StaminaBarFill
		\item RectTransform MedKit
		\item RectTransform PowerUpFill
		\item Text CurrentAmmo
		\item HealthComponent healthComponent
		\item PlayerController playerController
		\item PowerupBase powerUp
		\item uint health
		\item uint maxHealth
		\item float xScaleHP
		\item float xScaleStamina
		\item float HPIncrement
		\item uint previousHP
		\item uint lerpToHP
		\item float HealthBarSpeed
		\item bool medKitToggle
		\item float previousStamina
		\item float lerpToStamina
		\item float staminaIncrement
	\end{itemize}
	Methods
	\begin{itemize}
		\item Start
		\item Update
		\item DrawHealthBar
		\item DrawStaminaBar
	\end{itemize}
\end{itemize}

\subsection{Control Loop}
Unity handles everything that has to do with the control loop.

\subsection{Data Flow}
Unity handles the storing and loading of all files and assets. Every component written by the dev team should aim to load everything that is going to be used frequently into memory during the loading phase in the unity Start() and Awake() functions.

\subsection{Game Physics and Statistics}
\subsubsection{LevelBuilder}
The LevelBuilder Start() method should only happen on the server. When spawning a new room as the host, you need to specify that with Mirror.
\newline 
\newline Start
\begin{indentall}
All room modules that may be included in the level generation are provided in the Modules game object array with an exception of the start and goal rooms, which are provided separately as StartModule and GoalModule. Once the LevelBuilder is started, the level is generated in its entirety. It is however required that the start and goal rooms are reachable from each other.
\end{indentall}

\subsubsection{ItemSpawner}
The ItemSpawner is run when all rooms have spawned in. It runs once per rooms and spawns items correctly parented to avoid issues when moving rooms.
\newline 
\newline Awake
\begin{indentall}
Adds all weapon prefabs to the weapons list.
\end{indentall}
FindSnapPoints
\begin{indentall}
Finds all Snappoints in the current room. After first time, just return the points without the search.
\end{indentall}
SpawnItems
\begin{indentall}
Gets all potential spawners, then choses a set number of them to spawn a item, by silently clamping the set percentige then randoming a item or weapon.
\end{indentall}
GetRandom
\begin{indentall}
Produces a list with length of num with unic random numbers between min and max.
\end{indentall}

\subsubsection{HealthComponent}
The Health attribute should be synced with Mirror, meaning all methods changing health must be synced (Heal \& Damage must happen on the server)
\newline 
\newline Damage
\begin{indentall}
Damage is a method used for removing health from the Health attribute in HealthComponent. It takes the amount of health to lose as a parameter. This function is called from either the WeaponComponent on the player or from the enemy if it does damage to a player. If the health reaches zero upon taking damage, some action need to be handled, i.e. the player downing, spawner exploding or enemy dying. This is done using by registering actions using AddDeathAction.
\end{indentall}
Revive
\begin{indentall}
Revive is a method used for restoring the health to a certain state. The health is always restored to MaxHealth * MaxReviveRatio.
\end{indentall}
AddDeathAction
\begin{indentall}
Registers a new action used when the health reaches zero.
\end{indentall}
RemoveDeathAction
\begin{indentall}
Unregisters a registered action.
\end{indentall}

\subsubsection{PlayerController}
The player must be synced with Mirror. Internal variables such as ammo and movementSpeed does not unless implementing anti-cheat.
\newline 
\newline Update
\begin{indentall}
Handles player movement using inputs. Limits velocity according to the MovementSpeed. 
\end{indentall}
OnInteractBegin
\begin{indentall}
The interactor attempts to start reviving the player if below zero health. The function also verifies that the interactor has a medkit to perform this action. The revive action is not instant, but instead uses the ReviveTime attribute.
\end{indentall}
OnInteractEnd
\begin{indentall}
The interactor will stop the revive if not done already.
\end{indentall}
OnRaycastEnter
\begin{indentall}
If the player is downed and the player that is looking at the downed player has med Med Kit, show the interact tooltip.
\end{indentall}


\subsubsection{PowerUpBase}
PowerUpBase is used as a base class for all the individual puppet powerups.
\newline 
\newline OnActivate
\begin{indentall}
Override this function to specify behavior when the power up is activated. The activation will start the power up usage countdown using the Duration. The OnActivate function may be implemented as a coroutine to simplify logic.
\end{indentall}
OnComplete
\begin{indentall}
Override this function to specify behavior when the power up is suspended. The completion function may for example remove the Pekko’s goal icon from the compass.
\end{indentall}

\subsubsection{StaminaPower : PowerUpBase}
Froggo's individual powerup. Increases speed and stamina to allow Froggo to run through traps before they are activated. Inherits from PowerUpBase.

\subsubsection{InvisibilityPower : PowerUpBase}
Gekko's individual powerup. Makes Gekko invisible by changing shaders for puppets and puppeteer. Puppets will see a different color while puppeteer sees nothing. Inherits from PowerUpBase.

\subsubsection{NavigationPower : PowerUpBase}
Pekko's individual powerup. Shows the direction of the goal on the Compass by adding a new target to the CompassComponent. Inherits from PowerUpBase.

\subsubsection{SnifferPower : PowerUpBase}
Doggo's individual powerup. Shows if every door is locked by displaying a colored paw-print on the doors. Red for locked, green for unlocked. Inherits from PowerUpBase.

\subsubsection{GrabTool}
Update
\begin{indentall}
Checks all inputs relevant to the grabbing and dropping mechanic of the puppeteer and calls the relevant methods depending on the output. Also updates the currently selected room and placement guide depending on mouse/VR hover.
\end{indentall}
Pickup
\begin{indentall}
Pickup works with both items such as spawners and traps, and also rooms. For rooms specific rules need to be followed: Pickup picks up the selected room from the puppeteers perspective. The pickup function creates a copy of the selected object that can be lifted from the ground. The source object is however still in place until a new position is fully selected. Furthermore, a guidance object is also created from a lightweight clone of the source object that acts as an outline and views the most optimal placement option.
\end{indentall}
Drop
\begin{indentall}
Drop has to do different checks depending on if you are holding a room or just a trap/spawner. For a room, it drops the picked up room into the most optimal position in the level layout, if any. When a room is dropped, the selected object clone and its guide object is destroyed. If a dropped room does not fulfill all rules for connecting (using the CanConnect function), it is discarded.
\end{indentall}
CanConnect
\begin{indentall}
Returns a bool telling whether or not a room can be dropped in a certain place. The function should handle all placement rules. A source anchor point and destination anchor point should be provided. To modify the maximum snapping distance between anchors, the SnapDistance property is used. The connection rules are:
\begin{itemize}
	\item Both anchors must be valid.
	\item Anchors must be open for connection (not already used).
	\item The forward vector of the anchors must be opposite of each other.
	\begin{itemize}
		\item Vector3.Dot(srcForwardNormalized, dstForwardNormalized) == -1
	\end{itemize}
	\item The distance between the anchors must be less than the SnapDistance.
	\begin{itemize}
		\item Vector3.Distance(srcPosition, dstPosition) < SnapDistance
	\end{itemize}
\end{itemize}
\end{indentall}
FindNearestAnchor
\begin{indentall}
Locates the nearest anchor (door) to the selected object, if any.
\end{indentall}

\newpage

\subsubsection{ItemGrabTool}
Start
\begin{indentall}
Gets all the components and values needed.
\end{indentall}
SetPrices
\begin{indentall}
Sets up the HUD to display the correct cost for all items that can be placed.
\end{indentall}
Update
\begin{indentall}
Checks for inputs from the player and calls other functions depending on the input.
\end{indentall}
Pickup
\begin{indentall}
Instantiates the item you want to place add makes it follow your cursor.
\end{indentall}
Drop
\begin{indentall}
Places down the item on the position of the guide object.
\end{indentall}
FindNearestFreePoint
\begin{indentall}
Finds the nearest point on the map where the item can be placed
\end{indentall}
CanBePlaced
\begin{indentall}
Checks if the item can be placed down on the current snap point.
\end{indentall}

\subsubsection{InteractionController}
Update
\begin{indentall}
The update function raycasts straight ahead and looks for objects with the Interactable component. In case the player presses the Use button, an interaction is started. If a player hits an object with the Interactable component the OnRaycastEnter function is called.
\end{indentall}

\subsubsection{PathfinderComponent}
MoveTo
\begin{indentall}
Pathfinds to coordinates specified in parameter.
\end{indentall}
Update
\begin{indentall}
Follows the current path by steering/rotating the object and moving it forwards. If no path exists, do nothing.
\end{indentall}
Stop
\begin{indentall}
Aborts the current pathfinding
\end{indentall}

\subsubsection{StateMachine}
CheckProximity
\begin{indentall}
Checks for players nearby.
\end{indentall}
SetState
\begin{indentall}
Changes state.
\end{indentall}
Update
\begin{indentall}
Runs the current states Run function.
\end{indentall}

\newpage

\subsubsection{EnemySpawner}
Needs to be synced with Mirror
\newline
\newline Update
\begin{indentall}
Spawns an EnemyPrefab instance at the position of the member SpawnPoint whenever it's coroutine timer hits zero. The min-/maxDelay variables determin the range in which the spawntime can vary. Number of spawned minions per spawners is capped to the attribute MaxEnemySpawner. 
\end{indentall}

\subsubsection{WeaponComponent}
Use
\begin{indentall}
Attempts to fire the weapon. The function may immediately fail if there is no ammunition left or if the time since last weapon use does not exceed the firing speed. The weapon may also not be fired while reloading. In case the firing was successful, the following steps are performed:
\begin{itemize}
\item For each bullet in the total number of simultaneous bullet fired:
\begin{itemize}
\item Calculate bullet spread using the Spread variable
\item Raycast directly from the viewport center into the direction of the camera plus the angle deviation from the spread
\begin{itemize}
\item ViewportPointToRay(new Vector3(0.5f, 0.5f, 0.0f))
\end{itemize}
\item Collect the raycast hit information and fetch its HealthComponent
\item If there is a health component, deal some damage using the Damage variable
\item Create bullet impact effect or other effect
\end{itemize}
\item Play appropriate firing animation and effects
\item Perform recoil physics on the weapon
\item Play appropriate weapon firing sound
\item Reset firing speed timer
\item Decrease ammunition count
\end{itemize}
\end{indentall}
Reload
\begin{indentall}
Reloads the weapon using the ammunition the weapon owner is carrying. The function attempts to fill the weapon to its maximum Capacity, if possible. If the weapon is fully loaded, its LiquidLeft will equal its Capacity. A reload sound and animation is also played.
\end{indentall}
OnInteractBegin
\begin{indentall}
The interactor picks up this weapon. If the interactor already has a weapon component attached, the new weapon is automatically swapped for the new one. Some logic is required here to properly attach transforms between weapon and interactor.
\end{indentall}
OnRaycastEnter
\begin{indentall}
Shows the interact tooltip to the player that is looking at the weapon.
\end{indentall}

\newpage

\subsubsection{TrapComponent}
Must be synced with Mirror.
\newline
OnTriggerEnter
\begin{indentall}
Override this function in the subclass for detecting when a game object is within the trap activation area. The function shall immediately trigger the TrapTimer function. If the timer reaches ActivationTime, the trap and activation animation is activated and is therefore considered consumed.
\end{indentall}
OnTriggerExit
\begin{indentall}
Override this function in the subclass for detecting when a game object leaves the trap activation area. The function shall be used for handling damage on targets when the trap is activated.
\end{indentall}
TrapTimer
\begin{indentall}
This timer is started when a puppet enters the collider and is used for activating the trap after an amount of time. When the timer runs out it will start the animation for the trap.
\end{indentall}
DestroyTimer
\begin{indentall}
This timer is started when the trap has activated and the animation has finished. When the timer runs out it will destroy the object for the trap.
\end{indentall}
ActivateTrap
\begin{indentall}
Override this function in the subclass for handling the activation of the trap and damaging the puppet(s) inside, starting the DestroyTimer and other optional functionality. Function is often called in within the animation in an animation event.
\end{indentall}
DestroyTrap
\begin{indentall}
Override this function in the subclass for handling the destroying of the trap object after the DestroyTimer is done.
\end{indentall}

\subsubsection{BasicTrap}
Is placed on basic traps such as spikes and chandelier.

\subsubsection{BearTrap and BearInteract}
Both is placed on bear trap. BearTrap is used for the collider part of the logic, and BearInteract for the interaction logic once the trap has been activated by BearTrap.

\subsubsection{FakeItem}
Is placed on FakeItem for the interactable logic. Since it will relate more to a useable object than previous traps and does not activate upon entering its collider it does not use TrapComponent

\subsubsection{SnapFunctionality}
Is placed on all placeable traps for identifying with the item placement for the Puppeteer.

\newpage

\subsubsection{DoorComponent}
Must be synced with Mirror.
\newline
\newline Update
\begin{indentall}
Checks if the door should open or close depending on its current state.
\end{indentall}
OnInteractBegin
\begin{indentall}
Toggles the door from the open and closed positions. The door may not be opened when the attribute Locked is set to true. The rotation of the door is determined by the position of the interactor, meaning it may rotate both inwards and outwards. When the attribute Locked is set to false the door is instantly closed while normally the door opens smoothly.
\end{indentall}

\subsubsection{Interactable}
OnInteractBegin
\begin{indentall}
Override this function in the subclass for handling interaction events.
\end{indentall}
OnInteractEnd
\begin{indentall}
Override this function in the subclass for handling end of interaction events.
\end{indentall}
OnRaycastEnter
\begin{indentall}
Override this function in order to use the interaction tooltip
\end{indentall}
OnRaycastExit
\begin{indentall}
Disables the outline of the object.
\end{indentall}
ShowToolTip
\begin{indentall}
Shows the interaction tooltip for the player that is looking at an interactable object.
\end{indentall}

\subsubsection{CompassComponent}
AddObject
\begin{indentall}
Registers a new ‘trackable’ entity to the compass, e.g. teammates or level objects. Accepts any GameObject as parameter as long as it contains some Icon component.
\end{indentall}
RemoveObject
\begin{indentall}
Unregisters a game object from the list.
\end{indentall}
Update
\begin{indentall}
Updates all relative positions of the registered objects in the compass user interface. The icon of each object is displayed in the compass UI element. The compass is configured using some predefined ‘north’ direction. Some nitty gritty maths is here required to map 3D direction vectors to the 2D user interface element.
\end{indentall}

\subsubsection{PowerupRecharge}
Must be synced with Mirror.
\newline
\newline OnInteractBegin
\begin{indentall}
Refills the player’s power if applicable.
\end{indentall}

\subsubsection{MedkitComponent}
Must be synced with Mirror.
\newline
\newline OnInteractBegin
\begin{indentall}
Adds the medkit to the player’s inventory if the player doesn’t have one.
\end{indentall}
OnRaycastEnter
\begin{indentall}
Show the interact tooltip if the player does not already have a med kit in its inventory.
\end{indentall}

\subsubsection{HUD}
Start
\begin{indentall}
Load all the components needed to draw the HUD to the screen, they are loaded inside the start function instead of the update to increase performance.
\end{indentall}
Update
\begin{indentall}
Draw all the information about powerups, health, medkits, and stamina to the screen, images are scaled to represent the health and stamina and the scale is lerped to create smooth transitions.	
\end{indentall}

\newpage

\subsection{Artificial Intelligence}
The enemies are controlled by a simple Finite State Machine(FSM):
\newline
\newline States
\begin{itemize}
	\item AttackingState
	\item ReturnToSpawnerState
	\item WanderState
	\item SeekState
	\item IdleState
	\item BigAttackState
	\item ChargeAttackState
\end{itemize}
AttackingState
\newline
The enemies enter the attacking state when they have a clear line of sight of the player and they are within range. While in this state the enemies follow the player and automatically attack them when within range.
\newline
\newline ReturnToSpawnerState
\newline
When the spawner that spawned an enemy is attacked all the spawned enemies will enter this state and return to the spawner in order to protect it. When a spawner or an enemy is moved by the puppeteer this behavior is lost.
\newline
\newline WanderState
\newline
When an enemy doesn’t see any players it will wander on its own to nearby rooms to search for players.
\newline
\newline SeekState
\newline
This state will pathfind to a players last known location.
\newline
\newline IdleState
\newline
This state happens between wandering and makes the minion wait for an amount of time between two values.
\newline
\newline BigAttackState
\newline
The attack state for the tank. The tank can never lose its target unless it dies or turns invisible so it follows and attack when possible.
\newline
\newline ChargeAttackState
\newline
The tanks special attack, an accelerating charge at its target. The tank doesn't stop until the target is hit or the tank dies. It does damage depending on the tanks speed.

\subsection{Multiplayer}
Mirror by vis2k solves all of our multiplayer issues. The data is sent using TCP and a client-host system.

\section{User interface}
\subsection{Game Shell}
\begin{itemize}
	\item Splash screen
	\newline The first screen you see when you open the game. After any button is pressed, the menu should be opened.
	\item Main menu
	\newline The main menu is just a way to get to the other menus.
	\item Video options
	\newline Video options is where you can change resolution and enable/disable fullscreen.
	\item Audio options
	\newline Audio options should implement sound sliders for all types of sound in the game.
	\item Controls
	\newline In controls you should be able to rebind all keys used in the game and also change the sensitivity of the mouse.
	\item Join
	\newline In Join you enter an IP-address to connect to a host and enter a lobby
	\item Lobby
	\newline In a lobby you choose character and indicate when you are ready to start the game
	\item Host/Lobby
	\newline The same as ordinary lobby but for the host of the game.
\end{itemize}

\subsection{Main Play Screens}
Puppet
\begin{itemize}
	\item Health from the HealthComponent displayed as a number.
	\item Stamina from the PlayerController displayed as a bar.
	\item Ammunition from PlayerController displayer as a number.
	\item Power-up status displayed as a bar.
	\item Compass that points towards other game objects using their transforms to calculate angles.
	\begin{itemize}
		\item Also displays cardinal directions relative to some fixed point.
		\item Uses unique icons to represent different game objects, such as players.
	\end{itemize}
	\item Ammunition and Capacity from the equipped weapon as numbers
\end{itemize}
Puppeteer
\begin{itemize}
	\item Cooldown on rooms from CooldownComponent
	\item Room selection highlights calculated by the GrabTool
	\begin{itemize}
		\item Uses some outline shader to display optimal room placement and the selected room’s previous position.
	\end{itemize}
\end{itemize}

\section{Art and Video}
Unity handles loading, storing and drawing of the art. The animation transitions are done using an Animator Controller.
\section{Graphics Engine}
Unity handles all graphics rendering in the game.
\section{Artist Instructions}
Use file formats supported by Unity. Otherwise they have free hands.
\section{Sound and Music}
Unity has built in support for all the standard audio formats. Sounds are played by an Audio Source and they are picked up by an audio listener which is normally placed on the player’s camera. 3D sound, filters, and drop-off are all controlled inside the audio source.
\subsection{Sound Engineering Instructions}
Use file formats supported by Unity. Otherwise they have free hands. FMOD will be used.
\section{Level Specific Code}
The level is randomly generated at the start of the game to get a different layout each time. This is done using the LevelBuilder component in the Level game object. It is required that the start and goal rooms always are reachable after each level generation.


\end{document}